Elaboration with First-Class Implicit Function Types

### 2020-02-18 paper.tex
stuff

\subsubsection{On soundness, completeness, and other properties}
We briefly discuss what we can and cannot say about the presented
elaborator. First, elaboration is \emph{sound} in the sense that it never
produces malformed core syntax.

\begin{theorem}[Soundness of elaboration] The definitions of $\echeckblank$ and
$\einferblank$ conform to the specification \ref{TODO}. This follows by induction on surface syntax and analyzing the definitions, while also relying on properties of substitution, metasubstitution, $\unify$ and $\mathsf{freshMeta}$. \qed
\end{theorem}

@@

\todo{Say something about termination of elab?}

>>>>

\subsubsection{On soundness, completeness, and other properties}
We briefly discuss what we can say about the presented elaborator. First,
elaboration is \emph{sound} in the sense that it never produces malformed core
syntax.

\begin{theorem}[Soundness of elaboration] The definitions of $\echeckblank$ and
$\einferblank$ conform to the specification \ref{TODO}. This follows by
  induction on surface syntax, while also relying on the properties of
  substitution, metasubstitution, $\mathsf{insert}$, $\unify$ and
  $\mathsf{freshMeta}$. \qed
\end{theorem}

@@

\todo{polymorphic subtyping, starting and ending elaboration}
